---
title: "NOBO_GoalSetting"
author: "Sage Grey"
date: "6/23/2021"
output: html_document
---
# NOBO interactive Map: GCT & Trend Data
## This document creates a leaflet map showing goals collected as part of the Northern Bobwhite, Grasslands and Savannas National Partnership along side data collected showing NOBO trends collected by James Martin


### Loading Libraries
```{r setup, message=FALSE}
library(tidyverse)
library(sf)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(raster)
library(gstat)
library(spatial)
library(dplyr)
library(jsonlite)
library(ggplot2)
library(hrbrthemes)
library(ggthemes)
library(rgdal)

options(scipen=999)
```



### Loading Variable Sets

```{r, message = FALSE}


##Loading Boundaries
State_Boundaries <- st_read("cb_2018_us_state_500k.kml", quiet = TRUE)
State_Boundaries_GJSON <- st_read("US_State_Boundaries.json", quiet = TRUE)
State_Boundaries_Zip <- st_read("C:/Users/sageg/Desktop/newRrepo/USDA_WLFW_NOBO/StateBoundariesZIP", quiet = T)


#loading counties
natl_priority_map<-readOGR("C:/Users/sageg/Desktop/NOBO_Boundary_Aug2021_Dissolve_ST_Draft", layer="NOBO_Boundary_Aug2021_Dissolve_ST_Draft")



##Loading GCT Data
GCT_data <- read_csv("NOBODATA_ForLeaflet_Final.csv")

##Loading RDS
bird_data <- readRDS("NOBO_route_level_trends.rds")


##Loading RDS
bird_data <- readRDS("NOBO_route_level_trends.rds")

bird_data<-as(bird_data, "Spatial")  #this converts the object, bird_data, into a SpatialPointsDataFrame






# proj4string(bird_data)<-"+proj=laea +lat_0=40 +lon_0=-95 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"  ## if proj4string() is NA, you can define a projection.  IT HAS TO BE THE PROJECTION THAT IT WAS SUPPOSED TO HAVE ORIGINALLY

## convert the projection
bird_dat<-spTransform(bird_data, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))


transf_natl_PA <- spTransform(natl_priority_map, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))

```





### Adding Geometries to GCT Data

```{r, message = FALSE}

##Joining Boundaries and GCT Data
GCT_and_Geographies <- st_as_sf(left_join(GCT_data, State_Boundaries_Zip, by =c("STATE" ="NAME")))

 
```


### Creating Label for GCT Data

```{r, message=FALSE}

## Creating Label for States
GCT_and_Geographies$label <- 
  paste("<b>", "<big>", GCT_and_Geographies$STATE,"</b>", "</big>",
       "<br>", GCT_and_Geographies$REGION,
        "<br>", "Values shown below reflect the combined value of", "<br>", "Original Program Goals and Framework Goals",
       "<br>",
        "<br>",
        "<b> Top 3 Core Conservation Practices: </b>",
       "<br>",
        GCT_and_Geographies$TOP3CORE,
        "<br>",
       "<br>",
        "<b>", "Financial Assistance:", "</b>","<br>",
        "$ ", prettyNum(GCT_and_Geographies$REQFIN_FRAME,big.mark=","),
       "<br>",
        "<br>",  "<b>", "Total CP Coverage, Acres:", "</b>",
        "<br>", "Core:", prettyNum(GCT_and_Geographies$ACRE_FRAME_CORE, big.mark = ","),
        "<br>", "Supplemental:", prettyNum(GCT_and_Geographies$ACRE_FRAME_SUPP, big.mark = ","),
        "<br>", "Core and Supp Combined:", prettyNum(GCT_and_Geographies$ACRE_FRAME_CAS, big.mark = ","),
       "<br>",
        "<br>", "<b>", "Total CP Coverage, Feet:", "</b>",
        "<br>", "Core:", prettyNum(GCT_and_Geographies$FT_FRAME_CORE, big.mark = ","),
        "<br>", "Supplemental:", prettyNum(GCT_and_Geographies$FT_FRAME_SUPP, big.mark = ","),
        "<br>", "Core and Supp Combined:", GCT_and_Geographies$FT_FRAME_CAS,
       "<br>",
        "<br>", "<b>", "Total CP Coverage, Number of X:", "</b>",
        "<br>",GCT_and_Geographies$X_FRAME,
       "<br>",
        "<br>", "<b>", "Number of Written Plans:", "</b>",
        "<br>",GCT_and_Geographies$WRITTEN_FRAME,
       "<br>",
        "<br>", "<b>", "Number of Applied Plans:", "</b>",
        "<br>",GCT_and_Geographies$APPLIED_FRAME) %>% 
  lapply(htmltools::HTML)



# Creating Label for NOBO Trend Data
bird_dat$label <- 
  paste("NOBO Trend Data","<br>", "Abundance:", round(bird_dat$abund, digits=3),"<br>","Trend:", round(bird_dat$trend, digits=3),"</b>")%>%
  lapply(htmltools::HTML)

```


## Leaflet Map in Development

```{r, message = FALSE}

# create color coded dots

bins <- seq(min(bird_dat$trend),
             max(bird_dat$trend), by = .25)
# colramp<-colorRampPalette(c("red", "yellow", "blue"))
# cols<-colramp(length(bins))

pal <- colorNumeric("magma", 
                    domain = bins,
                    na.color = "#00000000")

scale_fill_brewer(palette="RdYlGn")

# setup Leaflet
leaflet(options=leafletOptions(minZoom = 4)) %>%
  addProviderTiles(providers$Stamen.Terrain) %>%
  addProviderTiles("Esri.WorldImagery", group="Aerial") %>% 
  
#create layer toggle  
  addLayersControl(
    baseGroups = c("Map", "Aerial"),
    overlayGroups = c("Points", "States", "Priority Counties"), 
    position = "topleft"
  ) %>% 
 
  #Add State Data 
  addPolygons(data=GCT_and_Geographies,
    highlightOptions = highlightOptions(fillOpacity = 1, fillColor="cornsilk"),
              weight=1, 
              fillColor= "orange",
              color = "black",
              fillOpacity=.5,
              label = paste0(GCT_and_Geographies$STATE, " - ", GCT_and_Geographies$REGION), 
              popup=~label,
              group="States",
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "11px",
                direction = "auto")) %>% 
  
  # Add NOBO trend Data
  addCircles(data=bird_dat, 
             color = ~pal(trend), 
            # size=bird_dat$abund,
             opacity=0.8,# fillOpacity = 0.6,
             label=paste0("Trend: 2002-2019: ", round(bird_dat$trend,digits=3)), 
             popup=~label, 
             group="Points") %>%
  
    addPolygons(data=transf_natl_PA, 
             # popup= GCT_and_Geographies$label[GCT_and_Geographies$STATE==indiana_priority_map$State],
             # color=priority$color, fillOpacity=0.8,
              #label=priority$Priority,
              color="Black",
             fillColor = "red", 
             opacity = .5,
             weight =1,
              group="Priority Counties")%>%
  
  #set Max Bounds
  setMaxBounds(lng1=-100.791110603, 
               lat1= 20,
               lng2= -66.96466,
               lat2= 71.3577635769)
```


























































### Setting up Leaflet with only GCT Data
```{r, message=FALSE}
nobo_summary_leaflet <- leaflet(GCT_and_Geographies)%>%
  addProviderTiles(providers$Stamen.Watercolor) %>%
  addPolygons(highlightOptions = highlightOptions(fillOpacity = 1, fillColor="cornsilk"),
              weight=1, 
              fillColor= "darkseagreen",
              color = "black",
              fillOpacity=.5,
              label = ~GCT_and_Geographies$label, 
              labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "11px",
    direction = "auto")) %>%
  
    addControl("Northern Bobwhite, Grasslands, and Savannas National Partnership 2022-2026: Framework Goal Summary", position = "topright")

nobo_summary_leaflet 

saveWidget(nobo_summary_leaflet, file="NOBO_SUMMARY_LEAFLET.html")

```

### leaflet with both GCT and Trend Data
```{r, message=FALSE}

## Setting up LEaflet 
nobo_summary_leaflet <- leaflet()%>%
  addProviderTiles(providers$Stamen.Watercolor) %>%
  addPolygons(data=GCT_and_Geographies, 
              highlightOptions = highlightOptions(fillOpacity = 1, fillColor="cornsilk"),
              weight=1, 
              fillColor= "darkseagreen",
              color = "black",
              fillOpacity=.5,
              label = ~GCT_and_Geographies$label, 
              labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "11px",
    direction = "auto")) %>%
  
  ## Add lci-data
  addCircles(data=separated_coord_bird_data,
            lng = ~long, 
            lat = ~lat)%>%
  
    addControl("Northern Bobwhite, Grasslands, and Savannas National Partnership 2022-2026: Framework Goal Summary", position = "topright")

nobo_summary_leaflet 

#saveWidget(nobo_summary_leaflet, file="NOBO_SUMMARY_LEAFLET.html")


```






### Showing BirdData as GGPLOT and Leaflet
```{r, message=FALSE}

## ggplot
ggplot(bird_data, aes(color=lci_trend)) +
  geom_sf()

## leaflet

leaflet(separated_coord_bird_data) %>%
addProviderTiles("CartoDB.Positron") %>%
  addCircles(lng = ~long, 
            lat = ~lat, 
            color ="red")
  

```










