
---
title: "Northern Bobwhite, Grasslands and Savannas National Partnership: 2022-2026"
author: "Sage Grey"
date: "6/23/2021"
output:
html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    theme: cosmo
code_folding: hide
---


# Task list

*1. ABUNDANCE + TREND:*  Clean up binning/color of variables as they appear on map

  a. Look at model graph in "Leaflet Reference Material" Folder Route_level_trends.png. 
  b. Bin Abundance according to those intervals (25)
  c. Adjust trend so the color crosses at 0.
  
*2. ADJUST APPERANCE:* Spruce up overall appearance

a. Look at charts/figures in "Figures for NOBO Report" as model. 
b. Create "clues/helper text" for interpreting map.(ie, indication of what the priority areas are vs the state boundaries) 

HEX CODES:
YEllow: f0ce63
Orange: f57943
Blue: a1d5d1
Green: bfbb60
Black: 34252f

Font: Roboto

*3. ADD CONTACT INFO:*

a. Add partner contact info to labels


# *code*



## NOBO interactive Map: GCT & Trend Data
This document creates a leaflet map showing Conservation Goals collected as part of the Northern Bobwhite, Grasslands and Savannas National Partnership along side data collected showing NOBO trends collected by James Martin


### Loading Libraries
```{r setup, message=FALSE, results= 'hide'}

library(tidyverse)
library(sf)
library(leaflet)
library(leaflegend)
library(htmltools)
library(htmlwidgets)
library(raster)
library(gstat)
library(spatial)
library(dplyr)
library(jsonlite)
library(ggplot2)
library(hrbrthemes)
library(ggthemes)
library(rgdal)
library(RColorBrewer)

options(scipen=999)

setwd("C:/Users/mwill/OneDrive - Harvard University/Work/SageConsulting/USDA_WLFW_NOBO")
```


### Loading Variable Sets

```{r, message = FALSE, results='hide'}


##Loading Boundaries
State_Boundaries <- st_read("cb_2018_us_state_500k.kml", quiet = TRUE)
State_Boundaries_GJSON <- st_read("US_State_Boundaries.json", quiet = TRUE)
State_Boundaries_Zip <- st_read("StateBoundariesZIP", quiet = T)


#loading counties
#natl_priority_map<-readOGR("NOBO_Boundary_Aug2021_Dissolve_ST_Draft", layer="NOBO_Boundary_Aug2021_Dissolve_ST_Draft")


##Loading Goal Collection (GCT) Data
GCT_data <- read_csv("NOBODATA_ForLeaflet_Final.csv")


##Loading BIRD DATA RDS
bird_data <- readRDS("NOBO_route_level_trends.rds")

bird_data<-as(bird_data, "Spatial")  #this converts the object, bird_data, into a SpatialPointsDataFrame



## Converting Projection
bird_dat<-spTransform(bird_data, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))


#transf_natl_PA <- spTransform(natl_priority_map, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))

##Joining Boundaries and GCT Data
GCT_and_Geographies <- st_as_sf(left_join(GCT_data, State_Boundaries_Zip, by =c("STATE" ="NAME")))


```





### Creating Labels for GCT Data + Bird Data

```{r, message=FALSE}

## Creating Label for States
GCT_and_Geographies$label <- 
  paste("<b>", "<big>", GCT_and_Geographies$STATE,"</b>", "</big>",
       "<br>", GCT_and_Geographies$REGION,
        "<br>", "Values shown below reflect the combined value of", "<br>", "Original Program Goals and Framework Goals",
       "<br>",
        "<br>",
        "<b> Top 3 Core Conservation Practices: </b>",
       "<br>",
        GCT_and_Geographies$TOP3CORE,
        "<br>",
       "<br>",
        "<b>", "Financial Assistance:", "</b>","<br>",
        "$ ", prettyNum(GCT_and_Geographies$REQFIN_FRAME,big.mark=","),
       "<br>",
        "<br>",  "<b>", "Total CP Coverage, Acres:", "</b>",
        "<br>", "Core:", prettyNum(GCT_and_Geographies$ACRE_FRAME_CORE, big.mark = ","),
        "<br>", "Supplemental:", prettyNum(GCT_and_Geographies$ACRE_FRAME_SUPP, big.mark = ","),
        "<br>", "Core and Supp Combined:", prettyNum(GCT_and_Geographies$ACRE_FRAME_CAS, big.mark = ","),
       "<br>",
        "<br>", "<b>", "Total CP Coverage, Feet:", "</b>",
        "<br>", "Core:", prettyNum(GCT_and_Geographies$FT_FRAME_CORE, big.mark = ","),
        "<br>", "Supplemental:", prettyNum(GCT_and_Geographies$FT_FRAME_SUPP, big.mark = ","),
        "<br>", "Core and Supp Combined:", GCT_and_Geographies$FT_FRAME_CAS,
       "<br>",
        "<br>", "<b>", "Total CP Coverage, Number of X:", "</b>",
        "<br>",GCT_and_Geographies$X_FRAME,
       "<br>",
        "<br>", "<b>", "Number of Written Plans:", "</b>",
        "<br>",GCT_and_Geographies$WRITTEN_FRAME,
       "<br>",
        "<br>", "<b>", "Number of Applied Plans:", "</b>",
        "<br>",GCT_and_Geographies$APPLIED_FRAME) %>% 
  lapply(htmltools::HTML)



# Creating Label for NOBO Trend Data
bird_dat$label <- 
  paste("NOBO Trend Data","<br>", "Abundance:", round(bird_dat$abund, digits=3),"<br>","Trend:", round(bird_dat$trend, digits=3),"</b>")%>%
  lapply(htmltools::HTML)

bird_data2 <- st_as_sf(bird_dat)
typeof(bird_data2)
```


## Leaflet Map in Development

```{r, message = FALSE}

# create color  + size coded dots

# TREND
bins_trend <- seq(min(bird_dat$trend),
             max(bird_dat$trend), by = .25)


#binPal <- colorBin("viridis", domain = bins_trend)
  
numPal <- colorNumeric(brewer.pal(11, "Spectral"), bird_dat$trend)

#pal <-  colorNumeric(c("firebrick1","limegreen"), 
 #                   domain = bins_trend,
  #                  na.color = "#00000000")

#ABUND
bins_abund <- seq(min(bird_dat$abund),
                  max(bird_dat$abund), 
                  by = 10)


symbols_abund <- makeSizeIcons(
  pal = numPal, colorValues = bird_dat$trend,
  values = bird_dat$abund,
  shape = "circle",
  opacity = 1,
  baseSize = 1.5
)

#scale_fill_brewer(palette="RdYlGn")

# setup Leaflet
nobo_and_gct_leaflet <- leaflet(options=leafletOptions(minZoom = 4)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addProviderTiles("Esri.WorldImagery", group="Aerial") %>% 
  
#create layer toggle  
  addLayersControl(
    baseGroups = c("Map", "Aerial"),
    overlayGroups = c("Points", "States", "Priority Counties"), 
    position = "topleft"
  ) %>% 
 
  #Add State Data 
  addPolygons(data=GCT_and_Geographies,
    highlightOptions = highlightOptions(fillColor="green", fillOpacity=.3),
              weight=1, 
              fillColor= "blanchedalmond",
              color = "black",
              fillOpacity=.3,
              label = paste0(GCT_and_Geographies$STATE, " - ", GCT_and_Geographies$REGION), 
              popup=~label,
              group="States",
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "11px",
                direction = "auto")) %>% 
  
  # Add NOBO trend Data
#  addCircles(data=bird_dat, 
 #            color = ~pal(trend), 
  #          weight= ~abund/5,
   #          opacity=1,# fillOpacity = 0.6,
    #         label=paste("2002-2019:","Trend:", round(bird_dat$trend,digits=3),", Abundance: ", round(bird_dat$abund)), 
     #        popup=~label, 
      #       group="Points") %>%
  
  addMarkers(data = bird_dat,
             icon = symbols_abund,
             label=paste("2002-2019:","Trend:", 
                         round(bird_dat$trend,digits=3),", Abundance: ", 
                         round(bird_dat$abund)), 
             popup=~label, 
             group="Points") %>%
  
 #   addPolygons(data=transf_natl_PA, 
             # popup= GCT_and_Geographies$label[GCT_and_Geographies$STATE==indiana_priority_map$State],
             # color=priority$color, fillOpacity=0.8,
              #label=priority$Priority,
  #            color="Black",
   #          fillColor = "mediumpurple2", 
    #         opacity = .9,
     #        weight =1,
      #        group="Priority Counties")%>%
  
  #set Max Bounds
  setMaxBounds(lng1=-140.791110603, 
               lat1= 10,
               lng2= -40.96466,
               lat2= 81.3577635769) %>% 
  
addLegendNumeric("Trend\n2002-2019", pal= numPal, 
          values=c(-4,-3,-2,-1,0,1,2,3,4), decreasing = T,
          orientation = "vertical") %>%

addLegendSize(values = bird_dat$abund,
              color = "black",
              fillColor = "black",
              title = "Abundance",
              orientation = "vertical",
              baseSize = 1.5,
              shape = "circle")


nobo_and_gct_leaflet




saveWidget(nobo_and_gct_leaflet, file="GCT_and_TrendNOBO.html")
  


                    

```



























```{r}
hist(bird_dat$abund)
hist(bird_dat$trend)
```





























